Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-28 autovi_paper.qmd
add one paragraph for d

\begin{equation*} \label{eq:kl-1}
D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
\end{equation*}

@@

>>>>

\begin{equation} \label{eq:kl-1}
D_{KL} = \int_{\mathbb{R}^{n}}\log\frac{p(\boldsymbol{e})}{q(\boldsymbol{e})}p(\boldsymbol{e})d\boldsymbol{e},
\end{equation}

@@

Equation \ref{eq:kl-1} can be adapted to different forms to account for various model violations. For instance, in the case of a linear regression model where necessary higher-order predictors, $\boldsymbol{Z}$, and their corresponding parameter, $\boldsymbol{\beta}_Z$, are omitted, the distance measure can be expanded as follows:

\begin{equation*} \label{eq:kl-2}
D_{KL} = \frac{1}{2}\left(\boldsymbol{\mu}_z^\top(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right),
\end{equation*}

where $\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z$, $\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{X}(\boldsymbol{X}^\top\boldsymbol{X})^{-1}\boldsymbol{X}^\top$ and $\boldsymbol{X}$ is the design matrix of the regression model.

### 2024-11-28 autovi_paper.tex
add one paragraph for d

>>>>

Equation \ref{eq:kl-1} can be adapted to different forms to account for
various model violations. For instance, in the case of a linear
regression model where necessary higher-order predictors,
\(\boldsymbol{Z}\), and their corresponding parameter,
\(\boldsymbol{\beta}_Z\), are omitted, the distance measure can be
expanded as follows:

\begin{equation*} \label{eq:kl-2}
D_{KL} = \frac{1}{2}\left(\boldsymbol{\mu}_z^\top(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right),
\end{equation*}

where
\(\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z\),
\(\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{X}(\boldsymbol{X}^\top\boldsymbol{X})^{-1}\boldsymbol{X}^\top\)
and \(\boldsymbol{X}\) is the design matrix of the regression model.
